---
title: "StatComp20052"
author: 'Lief Lv'
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{StatComp20052}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Overview

__StatComp20052__ is a simple R package developed to compute the probability of exactly one of these events occurring, and to identify the most deviant observation for each row of x. Two functions are included, namely, _exactlyone_ and _findols_ . For each function, examples are given.
## Introduction to _exactlyone_ 

The source R code for _exactlyone_ is as follows:

***exactlyone***
```{r}
exactlyone <- function(p) {
  notp <- 1 - p
  tot <- 0.0
  for (i in 1:length(p))
    tot <- tot + p[i] * prod(notp[-i])
  return(tot)
}
```

## Introduction to _findols_ 

The source R code for _findols_ is as follows:

***findols***
```{r}
findols <- function(x) {
  findol <- function(xrow) {
    mdn <- median(xrow)
    devs <- abs(xrow - mdn)
    return(which.max(devs))
    }
  return(apply(x,1,findol)) 
}
```
